Galois Slicing as Differentiation

### 2025-07-11 main/definability.tex
[ tex ] fiddle with the definability text

\begin{theorem}
  \label{thm:language-definability}
  For all $\Gamma \vdash M : \tau$, where $\Gamma$ and $\tau$ are
  first-order, there exists a morphism
  $g \in \Fam(\LatGal)(\sem{\Gamma}_{\mathit{fo}},
  \sem{\tau}_{\mathit{fo}})$ such that
  $H(g) = (\cong) \circ \sem{\Gamma \vdash M : \tau} \circ (\cong)$,
  where the isomorphisms arise from
  \lemref{first-order-agreement-types}.
\end{theorem}

@@

\begin{remark}
  Note that even if we modified our base interpretation of semantic
  \GPS along the lines of \remref{further-structure} to give a refined
  version $\cat{G}$ of $\Fam(\LatGal)$, as long as there is a finite
  product and coproduct preserving functor
  $\cat{G} \to \Fam(\MeetSLat \times \JoinSLat^\op)$, then the
  analogous result to \thmref{language-definability} still holds.
\end{remark}

>>>>

\begin{theorem}
  \label{thm:language-definability}
  For all $\Gamma \vdash M : \tau$, with $\Gamma, \tau$ first-order,
  there exists
  $g \in \Fam(\LatGal)(\sem{\Gamma}_{\mathit{fo}},
  \sem{\tau}_{\mathit{fo}})$ such that
  $H(g) = (\cong) \circ \sem{\Gamma \vdash M : \tau} \circ (\cong)$,
  with the isomorphisms from \lemref{first-order-agreement-types}.
\end{theorem}

@@

\begin{remark}
  If we modified our base interpretation of semantic \GPS as suggested
  in \remref{further-structure} to give a refined version $\cat{G}$ of
  $\Fam(\LatGal)$, then if there is a finite bicartesian functor
  $\cat{G} \to \Fam(\MeetSLat \times \JoinSLat^\op)$, an analogous
  result to \thmref{language-definability} still holds.
\end{remark}
